Linear Optics Interferometry

### 2016-09-21 paper.tex
added colour codes
Suggested structure of document

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}

@@

\section{Linear Optics Quantum Computation}

\section{Boson-sampling}

>>>>

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}
\usepackage[dvipsnames]{xcolor}

\newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
\newcommand{\peter}[1]{{\color{YellowGreen}{#1}}}
\newcommand{\comment}[1]{{\color{blue}{#1}}}

@@

\sihui{Si-Hui can colour code things she adds like this}

\peter{And Peter can do it like this}

\comment{Let's add comments and questions like this}

\section{Mathematical Background}

\comment{Mathematical representation for LO networks, and very basic background on quantum optics}

\section{Optical Encoding of Quantum Information}

\subsection{Single-Photons}

\subsubsection{Polarisation}

\subsubsection{Dual-Rail}

\subsubsection{Time-Bins}

\subsection{Continuous-Variables}

\subsubsection{Coherent States}

\subsubsection{Squeezed States}

\section{Efficient Circuit Decompositions of Linear Optics Networks}

\comment{Discuss the Reck et al. decomposition}

\section{Experimental Implementation}

\subsection{State Preparation}

\subsubsection{Single-Photons}

\subsubsection{Bell Pairs}

\subsubsection{Coherent States}

\subsubsection{Squeezed States}

\subsection{Linear Optics Networks}

\subsubsection{Bulk Optics}

\subsubsection{Waveguides}

\subsubsection{Time-Bins}

\comment{Discuss fibre-loop architecture}

\subsection{Measurement}

\subsubsection{Photodetection}

\comment{Discuss number-resolved and bucket detectors, multiplexed detection, APDs, current micropillar detectors}

\subsubsection{Homodyning}

\section{Applications for Linear Optics Interferometry}

\subsection{Linear Optics Quantum Computation}

\subsection{Boson-Sampling}

\subsection{Quantum Metrology}

\comment{Discuss NOON states - Heisenberg limited}

\comment{Discuss MORDOR scheme}

\subsection{Encrypted Quantum Computation}

\section{State of the Art}

\comment{Discuss where experiments are at at the moment}
